Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-31 R_codes/turk1.Rnw
updated version with offsets

suppressMessages(require(plyr))
turker <- ddply(dat,.(id), summarise,
	n = length(id),
	correct = sum(response),
  gender=gender[1]
)

## if we include all correct percentages above 0.2 we get rid of any differences due to gender, age or schooling
included <- unique(turker$id[with(turker, correct/n >= 0.1)])

@@

dat$offset <- log(0.05/.95)
base <- lmer(response~ offset(offset) - 1 + effect + (effect|id) , data=dat, family=binomial())
anova(m0, base)
q11 <- qplot(ranef(base)[[1]][,1], binwidth=0.2)
q12 <- qplot(ranef(base)[[2]][,1], binwidth=0.2)
summary(base)

base.1 <- lmer(response~ effect + (effect|id) , data=dat, family=binomial())

m1 <- lmer(response~ effect + (1|id), data=dat, family=binomial())
anova(base, m1)

m1a <- lmer(response~ effect + gender + (1|id), data=dat, family=binomial())
m1b <- lmer(response~ effect + academic_study + (1|id), data=dat, family=binomial())
m1c <- lmer(response~ effect + age + (1|id), data=dat, family=binomial())

m2a <- lmer(response~ effect + mgender + (1|id), data=dat, family=binomial())

anova(m0, base,  m2a, m1a)
anova(base, m1,  m2a, m1b)
anova(base, m2a, m1c)

dat$alpha <- 0.05
m3c <- lmer(response~ offset(alpha)+effect -1 + age + (effect|id), data=dat, family=binomial())
anova(base, m2a, m1c, m3c)

# there's something in model m1c that's not explained by missingness alone - but it might be an artefact - there's nothing immediately visible in the estimates
@

>>>>

suppressMessages(require(plyr))
turker <- ddply(dat,.(id), summarise,
	n = length(id),
	correct = sum(response[p_value < 0.0002]),
  gotchance = sum(p_value < 0.0002),  
  pvalue = mean(p_value),  
  pcorrect = sum(response)/length(id),
  gender=gender[1]
)

## if we include all correct percentages above 0.2 we get rid of any differences due to gender, age or schooling

## Mahbub
# included <- unique(turker$id[with(turker, correct/gotchance > 0.5)])

@@

dat$offset <- log(0.05/.95)
base <- lmer(response~ offset(offset) - 1 + effect + (effect-1|id) , data=dat, family=binomial())

qqnorm(ranef(base)[[1]][,1])
q11 <- qplot(ranef(base)[[1]][,1], geom="histogram", binwidth=0.002)
q11

base.2 <- lmer(response~ offset(offset) - 1 + effect + (effect-1|id) , data=dat, family=binomial(link="probit"))
base.3 <- lmer(response~ offset(offset) - 1 + effect + (effect-1|id) , data=dat, family=binomial(link="cloglog"))
# 
anova(base.2, base.3, base)

m1a <- lmer(response~  offset(offset) - 1 + effect:mgender + (effect-1|id), data=dat, family=binomial())
m1b <- lmer(response~ offset(offset) - 1 + effect:academic_study + (effect-1|id), data=dat, family=binomial())
m1c <- lmer(response~ offset(offset) - 1 + effect:age + (effect-1|id), data=dat, family=binomial())

anova(base, m1a)
anova(base, m1b)
anova(base, m1c)

qplot(effect, fitted(m1a), data=dat, colour=factor(academic_study))
# there's something in model m1c that's not explained by missingness alone - but it might be an artefact - there's nothing immediately visible in the estimates
@
